Vulnerability Analysis of Container Images in Neuroimaging

### 2020-05-31 paper.tex
changed reference

\begin{table*}
  \caption{some table}
	\begin{tabular}{>|{\bfseries}c| c| c| *{4}{c|}}\hline
	  \multirow{2}{*}{\bfseries Image Labels} & 
	  \multirow{2}{*}{\bfseries Image Names} & 
	  \multirow{2}{*}{\bfseries OS} & 
	  \multicolumn{4}{c|}{\bfseries Vulnerabilities} \\\cline{2-5} 
                       & \textbf{A} & \textbf{C} & \textbf{V}  & \textbf{S} \\ \hline
a	& bids/example	& ubuntu:14.04	& 838	& 663	& 683	& \\ \hline
b	& bids/freesurfer	& ubuntu:14.04	& 353	& 215	& 192	& \\ \hline
c	& bids/ndmg	& ubuntu:14.04	& 934	& 757	& 782	& \\ \hline
d	& bids/broccoli:v1.0.0	& centos 6	& 79	& 79	& 117	& \\ \hline
e	& bids/fibredensityandcrosssection	& ubuntu:14.04	& 1086	& 849	& 868	& \\ \hline
f	& bids/spm	& ubuntu:14.04	& 191	& 246	& 235	& \\ \hline
g	& poldracklab/mriqc:0.15.0	& ubuntu:16.04	& 432	& 328	& 332	& \\ \hline
h	& bids/cpac:v1.0.1a\_22	& ubuntu:16.04	& 698	& 524	& 535	& \\ \hline
I	& bids/hyperalignment	& ubuntu:16.04	& 1717	& 1327	& 1433	& \\ \hline
j	& bids/mindboggle:0.0.4-1	& debian:8	& 671	& 955	& 569	& \\ \hline
k	& bids/mrtrix3\_connectome	& ubuntu:18.04	& 275	& 157	& 158	& \\ \hline
l	& bids/rs\_signal\_extract:0.1	& ubuntu:16.04	& 867	& 454	& 473	& \\ \hline
m	& bids/aa:v0.2.0	& ubuntu:14.04	& 189	& 244	& 233	& \\ \hline
n	& bids/niak	& ubuntu:16.04	& 1482	& 1366	& 1420	& \\ \hline
o	& bids/oppni:v0.7.0-1	& ubuntu:14.04	& 913	& 698	& 723	& \\ \hline
p	& poldracklab/fmriprep:unstable	& ubuntu:16.04	& 516	& 355	& 393	& \\ \hline
q	& bids/brainiak-srm	& ubuntu:16.04	& 897	& 484	& 503	& \\ \hline
r	& bids/nipypelines:0.3.0	& debian:8	& 641	& 878	& 451	& \\ \hline
s	& bids/hcppipelines:v3.17.0-18	& debian:8	& 526	& 873	& 620	& \\ \hline
t	& bids/magetbrain	& ubuntu:18.04	& 112	& 117	& 126	& \\ \hline
u	& bids/tracula:v6.0.0-4	& ubuntu:14.04	& 874	& 664	& 683	& \\ \hline
v	& bids/baracus	& ubuntu:14.04	& 172	& 238	& 216	& \\ \hline
w	& bids/antscorticalthickness:v2.2.0-1	& ubuntu:17.04	& 289	& 27	& no oval data	& \\ \hline 
x	& bids/dparsf:v4.3.12	& ubuntu:14.04	& 507	& 750	& 757	& \\ \hline
y	& bids/afni\_proc	& ubuntu:17.10	& 67	& 16	& no oval data	& \\ \hline
z	& bids/rshrf:1.0.1	& alpine:3.8.4	& 5	& 3	& 3	& \\ \hline
aa	& bids/ndmg:v0.1.0	& ubuntu 14.04	& 934	& 758	& 782	& \\ \hline
ab	& mcin/qeeg:latest	& centos 7	& 46	& 46	& 142	& \\ \hline
ac	& camarasu/creaphase:0.3	& centos 7	& 54	& 54	& 186	& \\ \hline
ad	& bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest	& centos 7	& 70	& 76	& 157	& \\ \hline
ae	& mcin/docker-fsl:latest	& centos 7	& 75	& 75	& 201	& \\ \hline
af	& gkiar/onevoxel:v0.3.0rc2	& alpine 3.7.1	& 5	& 2	& 2	& \\ \hline
ag	& bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest	& centos 7	& 70	& 76	& 157	& \\ \hline 
ah	& bt5e/ants:latest	& centos 7	& 150	& 156	& 336	& \\ \hline
ai	& poldracklab/fmriprep:1.2.3	& ubuntu 16.04	& 591	& 441	& 447	& \\ \hline
aj	& gkiar/dwipreproc\_fsl-5.0.11\_minified	& ubuntu 16.04	& 391	& 258	& 263	& \\ \hline
ak	& gkiar/mask2boundary:v0.1.0	& alpine 3.9.0	& 15	& 11	& 11	& \\ \hline
al	& mcin/ica-aroma:latest	& centos 7	& 75	& 75	& 202	& \\ \hline
am	& c3genomics/genpipes	& 	& 	& 	& 	& 99 \\ \hline
an	& bioinformatics-group/aqua-singularity-recipe	& 	& 	& 	& 	& 7 \\ \hline
ao	& MontrealSergiy/BEst	& 	& 	& 	& 	& 106 \\ \hline
ap	& shub://aces/cbrain-containers-recipes:fsl\_v6.0.1	& 	& 	& 	& 	& 206 \\ \hline
aq	& shots47s/bids-freesurfer-6.0	& 	& 	& 	& 	& 212 \\ \hline
ar	& shots47s/bids-fmriprep-1.2.3	& 	& 	& 	& 	& 453 \\ \hline
  \end{tabular}
  \end{table*}

@@

\textbf{False positives by Clair:} These vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
present inside the image but Clair is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
Clair is only referring to Ubuntu 14.04 ESM release. For example CVE-2019-1274. \change{The reasons of Clair showing
false positives and false negatives are unclear. We reported this issue on two Google groups of Clair i.e CoreOS Dev and
clair-dev (\href{https://groups.google.com/forum/#!topic/clair-dev/8IqCCfd-EEc}{https://groups.google.com/forum/#!topic/clair-dev/8IqCCfd-EEc}).
However, we did not receive any reply from developers.}

>>>>

%\begin{table*}
%  \caption{some table}
%	\begin{tabular}{>|{\bfseries}c| c| c| *{4}{c|}}\hline
%	  \multirow{2}{*}{\bfseries Image Labels} & 
%	  \multirow{2}{*}{\bfseries Image Names} & 
%	  \multirow{2}{*}{\bfseries OS} & 
%	  \multicolumn{4}{c|}{\bfseries Vulnerabilities} \\\cline{2-5} 
%                       & \textbf{A} & \textbf{C} & \textbf{V}  & \textbf{S} \\ \hline
%a	& bids/example	& ubuntu:14.04	& 838	& 663	& 683	& \\ \hline
%b	& bids/freesurfer	& ubuntu:14.04	& 353	& 215	& 192	& \\ \hline
%c	& bids/ndmg	& ubuntu:14.04	& 934	& 757	& 782	& \\ \hline
%d	& bids/broccoli:v1.0.0	& centos 6	& 79	& 79	& 117	& \\ \hline
%e	& bids/fibredensityandcrosssection	& ubuntu:14.04	& 1086	& 849	& 868	& \\ \hline
%f	& bids/spm	& ubuntu:14.04	& 191	& 246	& 235	& \\ \hline
%g	& poldracklab/mriqc:0.15.0	& ubuntu:16.04	& 432	& 328	& 332	& \\ \hline
%h	& bids/cpac:v1.0.1a\_22	& ubuntu:16.04	& 698	& 524	& 535	& \\ \hline
%I	& bids/hyperalignment	& ubuntu:16.04	& 1717	& 1327	& 1433	& \\ \hline
%j	& bids/mindboggle:0.0.4-1	& debian:8	& 671	& 955	& 569	& \\ \hline
%k	& bids/mrtrix3\_connectome	& ubuntu:18.04	& 275	& 157	& 158	& \\ \hline
%l	& bids/rs\_signal\_extract:0.1	& ubuntu:16.04	& 867	& 454	& 473	& \\ \hline
%m	& bids/aa:v0.2.0	& ubuntu:14.04	& 189	& 244	& 233	& \\ \hline
%n	& bids/niak	& ubuntu:16.04	& 1482	& 1366	& 1420	& \\ \hline
%o	& bids/oppni:v0.7.0-1	& ubuntu:14.04	& 913	& 698	& 723	& \\ \hline
%p	& poldracklab/fmriprep:unstable	& ubuntu:16.04	& 516	& 355	& 393	& \\ \hline
%q	& bids/brainiak-srm	& ubuntu:16.04	& 897	& 484	& 503	& \\ \hline
%r	& bids/nipypelines:0.3.0	& debian:8	& 641	& 878	& 451	& \\ \hline
%s	& bids/hcppipelines:v3.17.0-18	& debian:8	& 526	& 873	& 620	& \\ \hline
%t	& bids/magetbrain	& ubuntu:18.04	& 112	& 117	& 126	& \\ \hline
%u	& bids/tracula:v6.0.0-4	& ubuntu:14.04	& 874	& 664	& 683	& \\ \hline
%v	& bids/baracus	& ubuntu:14.04	& 172	& 238	& 216	& \\ \hline
%w	& bids/antscorticalthickness:v2.2.0-1	& ubuntu:17.04	& 289	& 27	& no oval data	& \\ \hline 
%x	& bids/dparsf:v4.3.12	& ubuntu:14.04	& 507	& 750	& 757	& \\ \hline
%y	& bids/afni\_proc	& ubuntu:17.10	& 67	& 16	& no oval data	& \\ \hline
%z	& bids/rshrf:1.0.1	& alpine:3.8.4	& 5	& 3	& 3	& \\ \hline
%aa	& bids/ndmg:v0.1.0	& ubuntu 14.04	& 934	& 758	& 782	& \\ \hline
%ab	& mcin/qeeg:latest	& centos 7	& 46	& 46	& 142	& \\ \hline
%ac	& camarasu/creaphase:0.3	& centos 7	& 54	& 54	& 186	& \\ \hline
%ad	& bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest	& centos 7	& 70	& 76	& 157	& \\ \hline
%ae	& mcin/docker-fsl:latest	& centos 7	& 75	& 75	& 201	& \\ \hline
%af	& gkiar/onevoxel:v0.3.0rc2	& alpine 3.7.1	& 5	& 2	& 2	& \\ \hline
%ag	& bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest	& centos 7	& 70	& 76	& 157	& \\ \hline 
%ah	& bt5e/ants:latest	& centos 7	& 150	& 156	& 336	& \\ \hline
%ai	& poldracklab/fmriprep:1.2.3	& ubuntu 16.04	& 591	& 441	& 447	& \\ \hline
%aj	& gkiar/dwipreproc\_fsl-5.0.11\_minified	& ubuntu 16.04	& 391	& 258	& 263	& \\ \hline
%ak	& gkiar/mask2boundary:v0.1.0	& alpine 3.9.0	& 15	& 11	& 11	& \\ \hline
%al	& mcin/ica-aroma:latest	& centos 7	& 75	& 75	& 202	& \\ \hline
%am	& c3genomics/genpipes	& 	& 	& 	& 	& 99 \\ \hline
%an	& bioinformatics-group/aqua-singularity-recipe	& 	& 	& 	& 	& 7 \\ \hline
%ao	& MontrealSergiy/BEst	& 	& 	& 	& 	& 106 \\ \hline
%ap	& shub://aces/cbrain-containers-recipes:fsl\_v6.0.1	& 	& 	& 	& 	& 206 \\ \hline
%aq	& shots47s/bids-freesurfer-6.0	& 	& 	& 	& 	& 212 \\ \hline
%ar	& shots47s/bids-fmriprep-1.2.3	& 	& 	& 	& 	& 453 \\ \hline
%  \end{tabular}
%  \end{table*}

@@

\textbf{False positives by Clair:} These vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
present inside the image but Clair is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
Clair is only referring to Ubuntu 14.04 ESM release. For example CVE-2019-1274. \change{The reasons of Clair showing
false positives and false negatives are unclear. We reported this issue on two Google groups of Clair i.e CoreOS Dev and
clair-dev \href{https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc}{(https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc).}
However, we did not receive any reply from developers.}
